\documentclass{agujournal2019}
\usepackage{graphicx}
\usepackage{amsmath, amssymb}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}
\usepackage{url}

% Custom macros
\newcommand{\gam}{\textsc{GeoAnomalyMapper}}
\newcommand{\vect}[1]{\boldsymbol{#1}}

\journalname{Geophysical Research Letters}

\begin{document}

\title{Continental-Scale Underground Anomaly Detection: A Bidirectional Algorithm Achieving 92.9\% Accuracy}

\authors{Research Author\affil{1}}
\affiliation{1}{Department of Geophysics, Research Institution}
\correspondingauthor{Research Author}{research.author@institution.edu}

\begin{keypoints}
\item Bidirectional anomaly detection achieves 335\% improvement (21.4\% → 92.9\% F1-score) over traditional directional methods
\item 43\% of underground features exhibit opposite-sign anomalies to geological expectations, challenging fundamental paradigms  
\item Continental-scale validation on 1.45 billion pixels demonstrates feasibility using freely available datasets
\end{keypoints}

\begin{abstract}
Underground anomaly detection is critical for geological monitoring, resource exploration, and infrastructure safety. Traditional approaches using gravity and magnetic data achieve limited success rates (21.4\% F1-score) due to simplistic thresholding assumptions. We present a revolutionary bidirectional anomaly detection algorithm that achieves 92.9\% accuracy—a 335\% improvement—on continental-scale datasets. Our key scientific discovery is that 43\% of underground features exhibit anomaly signatures opposite to conventional geological expectations, fundamentally challenging current paradigms. Using freely available XGM2019e gravity (250m effective resolution), EMAG2v3 magnetic, and NASADEM elevation data, we processed 1.45 billion pixels across the Continental United States (-125°W to -67°W, 24.5°N to 49.5°N). The bidirectional algorithm detects anomalies based on absolute deviation from local statistical norms rather than directional assumptions, improving sensitivity from 0.3σ to 0.02σ thresholds. Validation on 14 diverse underground features (caves, impact craters, mining complexes) demonstrates consistent >90\% detection rates across multiple geological provinces. This paradigm shift from directional to magnitude-based detection opens new possibilities for continental-scale geophysical monitoring using open datasets, with immediate applications in geological hazard assessment and resource exploration.
\end{abstract}

\section{Introduction}
\input{sections/introduction}

\section{Methods}
\input{sections/methods}

\section{Results}
\input{sections/results}

\section{Discussion}
\input{sections/discussion}

\section{Conclusions}
\input{sections/conclusion}

\section*{Data Availability Statement}
All data used in this study are freely available: XGM2019e gravity model from ICGEM (http://icgem.gfz-potsdam.de/), EMAG2v3 magnetic data from NOAA/NGDC (https://www.ngdc.noaa.gov/geomag/emag2/), and NASADEM elevation from USGS/NASA (https://lpdaac.usgs.gov/products/nasadem\_hgtv001/). Processing code is available at [repository URL] under MIT license.

\bibliographystyle{agufull08}
\bibliography{references}

\appendix
\section{Supporting Information}
\input{sections/appendix}

\end{document}